Figure 1 - overview

### 2024-08-06 ms_figure_1_overview.Rmd
Fix axis labels, use updated DBD family names (Fig1)

```{r load-dbd, class.source="fold-show"}
dbd <- read.delim(params$dbdtxt) |>
    dplyr::group_by(DBD_class, Conserved_human) |>
    dplyr::tally() |>
    dplyr::mutate(cons = ifelse(Conserved_human, "Conserved in human",
                                "Not conserved in human")) |>
    dplyr::group_by(DBD_class) |>
    dplyr::mutate(totn = sum(n)) |>
    dplyr::ungroup()
```

@@

```{r numbers-ipms, class.source="fold-show"}
## Number of NCBI Conserved Domains shown in the figure (excluding "Other")
length(setdiff(unique(dbd$DBD_class), "Other"))

@@

(gg_dbd <- ggplot(dbd, aes(x = fct_reorder(DBD_class, totn, .desc = TRUE), y = n, 
                           fill = cons)) + 
     geom_col() + 
     scale_fill_manual(values = c("Conserved in human" = lighten(main_colors[1], 0.3),
                                  "Not conserved in human" = main_colors[1]), 
                       name = "") + 
     labs(x = "DBD family (NCBI Conserved Domains)",
          y = "Number of\ntranscription factors") + 
     theme_cowplot() + 
     theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
           legend.position = "inside",
           legend.position.inside = c(0.55, 0.9)))
```

@@

ave_tpm <- data.frame(
    bait = allbaits, 
    bait_pulled = factor(
        ifelse(.capitalize(allexps) %in% nobait_150, 
               "Bait not pulled down (150 mM NaCl IP-MS)",
               "Bait pulled down (150 mM NaCl IP-MS)"),
        levels = c("Bait pulled down (150 mM NaCl IP-MS)",
                   "Bait not pulled down (150 mM NaCl IP-MS)")),
    tpm = rowMeans(assay(rnaseq, "abundance")[allbaits, 
                                              rnaseq$Group_name == "wt_WT_mRNA"])
)
gg_tpm <- ggplot(ave_tpm, aes(x = fct_reorder(bait, tpm, .desc = TRUE), y = tpm, 
                              color = bait_pulled)) + 
    geom_hline(yintercept = 0, linetype = "dashed", color = na_color) +
    geom_point(size = 1) + 
    theme_cowplot() + 
    theme(legend.position = "inside", legend.position.inside = c(0.15, 0.9)) +
    scale_color_manual(values = c("Bait pulled down (150 mM NaCl IP-MS)" = pt_color,
                                  "Bait not pulled down (150 mM NaCl IP-MS)" = na_color),
                       name = "") + 
    scale_x_discrete(breaks = c("mei4", "atf31", "atf21", "cuf2", "rsv1")) + 
    guides(color = guide_legend(nrow = 2, byrow = TRUE)) + 
    labs(x = "Transcription factors",
         y = "Transcription factor\ngene expression (TPM)")
(gg_tpm + theme(axis.text.x = element_blank(),
                axis.ticks.length.x = unit(2, "mm"),
                axis.ticks.x = element_line(color = main_colors[1],
                                            linewidth = 1.25)))
```

@@

cowplot::plot_grid(
    fig1c,
    cowplot::plot_grid(
        gg_dbd, 
        gg_tpm + theme(axis.text.x = element_blank(),
                       axis.ticks.length.x = unit(2, "mm"),
                       axis.ticks.x = element_line(color = main_colors[1],
                                                   linewidth = 1.25)),
        nrow = 1,
        labels = c("B", "C"),
        align = "vh",
        axis = "b"
    ),
    cowplot::plot_grid(
        gg_nbrint,
        gg_nbrpeaks_all_narrow_by_npeaks,
        nrow = 1, 
        labels = c("D", "E"),
        align = "vh", 
        axis = "b"
    ),
    nrow = 3,
    labels = c("A", NA, NA),
    align = "v",
    axis = "b",
    rel_heights = c(73, 50, 50)
)
```

@@

cowplot::plot_grid(
    gg_tpm + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + 
        labs(x = "") + geom_point(size = 3), 
    gg_nbrint_all,
    gg_nbrpeaks_all_wide,
    ncol = 1, 
    align = "v", 
    axis = "l",
    labels = c("A", "B", "C"),
    rel_heights = c(1, 1, 1)
)
```

>>>>

```{r load-dbd, class.source="fold-show"}
dbd <- read.delim(params$dbdtxt) |>
    dplyr::group_by(DBD_class_name, Conserved_human) |>
    dplyr::tally() |>
    dplyr::mutate(cons = ifelse(Conserved_human, "Conserved in human",
                                "Not conserved in human")) |>
    dplyr::group_by(DBD_class_name) |>
    dplyr::mutate(totn = sum(n)) |>
    dplyr::ungroup()
```

@@

```{r numbers-ipms, class.source="fold-show"}
## Number of NCBI Conserved Domains shown in the figure (excluding "Other")
length(setdiff(unique(dbd$DBD_class_name), "Other"))

@@

(gg_dbd <- ggplot(dbd, aes(x = fct_reorder(DBD_class_name, totn, .desc = TRUE), y = n, 
                           fill = cons)) + 
     geom_col() + 
     scale_fill_manual(values = c("Conserved in human" = lighten(main_colors[1], 0.3),
                                  "Not conserved in human" = main_colors[1]), 
                       name = "") + 
     labs(x = "DBD family (NCBI Conserved Domains)",
          y = "Number of\ntranscription factors") + 
     theme_cowplot() + 
     theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
           legend.position = "inside",
           legend.position.inside = c(0.55, 0.9)))
```

@@

ave_tpm <- data.frame(
    bait = allbaits, 
    bait_pulled = factor(
        ifelse(.capitalize(allexps) %in% nobait_150, 
               "Bait not pulled down (150 mM NaCl IP-MS)",
               "Bait pulled down (150 mM NaCl IP-MS)"),
        levels = c("Bait pulled down (150 mM NaCl IP-MS)",
                   "Bait not pulled down (150 mM NaCl IP-MS)", 
                   "Meiosis-specific transcription factors")),
    tpm = rowMeans(assay(rnaseq, "abundance")[allbaits, 
                                              rnaseq$Group_name == "wt_WT_mRNA"])
)
gg_tpm <- ggplot(ave_tpm, aes(x = fct_reorder(bait, tpm, .desc = TRUE), y = tpm, 
                              color = bait_pulled, shape = bait_pulled)) + 
    geom_hline(yintercept = 0, linetype = "dashed", color = na_color) +
    geom_point(size = 1, show.legend = TRUE) + 
    theme_cowplot() + 
    theme(legend.position = "inside", legend.position.inside = c(0.15, 0.9)) +
    scale_color_manual(values = c("Bait pulled down (150 mM NaCl IP-MS)" = pt_color,
                                  "Bait not pulled down (150 mM NaCl IP-MS)" = na_color,
                                  "Meiosis-specific transcription factors" = main_colors[1]),
                       drop = FALSE, name = "") + 
    scale_shape_manual(values = c("Bait pulled down (150 mM NaCl IP-MS)" = 16,
                                  "Bait not pulled down (150 mM NaCl IP-MS)" = 16,
                                  "Meiosis-specific transcription factors" = 15),
                       drop = FALSE, name = "") + 
    guides(color = guide_legend(nrow = 3, byrow = TRUE,
                                override.aes = list(size = 3))) + 
    labs(x = "Transcription factors",
         y = "Transcription factor\ngene expression (TPM)")
(gg_tpm + 
        geom_segment(data = ave_tpm |> filter(bait %in% c("mei4", "atf31", "atf21", "cuf2", "rsv1")),
                     aes(x = bait, xend = bait, y = -6, yend = -20), color = main_colors[1], 
                     linewidth = 1.25) + 
        scale_y_continuous(expand = expansion(mult = c(0, 0.025))) + 
        theme(axis.text.x = element_blank()))
```

@@

cowplot::plot_grid(
    fig1c,
    cowplot::plot_grid(
        gg_dbd, 
        gg_tpm + geom_segment(data = ave_tpm |> filter(bait %in% c("mei4", "atf31", "atf21", "cuf2", "rsv1")),
                              aes(x = bait, xend = bait, y = -6, yend = -20), color = main_colors[1], 
                              linewidth = 1.25) + 
            scale_y_continuous(expand = expansion(mult = c(0, 0.025))) + 
            theme(axis.text.x = element_blank()),
        nrow = 1,
        labels = c("B", "C"),
        align = "vh",
        axis = "b"
    ),
    cowplot::plot_grid(
        gg_nbrint,
        gg_nbrpeaks_all_narrow_by_npeaks,
        nrow = 1, 
        labels = c("D", "E"),
        align = "vh", 
        axis = "b"
    ),
    nrow = 3,
    labels = c("A", NA, NA),
    align = "v",
    axis = "b",
    rel_heights = c(73, 50, 50)
)
```

@@

cowplot::plot_grid(
    gg_tpm + geom_segment(data = ave_tpm |> filter(bait %in% c("mei4", "atf31", "atf21", "cuf2", "rsv1")),
                          aes(x = bait, xend = bait, y = -9, yend = -30), color = main_colors[1], 
                          linewidth = 3) + 
        scale_y_continuous(expand = expansion(mult = c(0, 0.025))) + 
        theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + 
        labs(x = "") + geom_point(size = 3),
    gg_nbrint_all,
    gg_nbrpeaks_all_wide,
    ncol = 1, 
    align = "v", 
    axis = "l",
    labels = c("A", "B", "C"),
    rel_heights = c(1, 1, 1)
)
```
